---
title: "Statistical Inference Project Part 1"
author: "Jacinto"
date: "April 2, 2016"
output:
  html_document:
    keep_md: yes
---

## Introduction
n this project you will investigate the exponential distribution in R and compare it with the Central Limit Theorem. The exponential distribution can be simulated in R with rexp(n, lambda) where lambda is the rate parameter. The mean of exponential distribution is 1/lambda and the standard deviation is also 1/lambda. Set lambda = 0.2 for all of the simulations. You will investigate the distribution of averages of 40 exponentials. Note that you will need to do a thousand simulations.

## Simulation
```{r}
set.seed(8080)
n <- 40; y <- .2; m <- 1:1000
meanSim <- sapply(m, function(x){mean(rexp(n,y))})
hist(meanSim)
```

## 1. Show the sample mean and compare it to the theoretical mean of the distribution
```{r}
## The center based on the model
sim <- mean(meanSim)
```
```{r}
## Theoretical mean of distribution
actual <- 1/.2
```
The mean of simulation is `r sim` and the theoretical mean is `r actual` and the difference is `r sim-actual`. As you can see the difference isn't large. The error is `r (sim-actual)/actual*100`%. If larger sample was simulated the error would be smaller, but this is good enough. 

```{r}
hist(meanSim)
abline(v=sim, col="red", lwd =1)
abline(v=actual, col="green", lwd=1)
legend("topright", c("Simulated Center", "Theoretical Center"), col=c("red", "green"), lwd=3)
```

## 2. Show how variable the sample is (via variance) and compare it to the theoretical variance of the distribution.
```{r}
sdSim <- sd(meanSim)
varSim <- var(meanSim)
sdActual <- (1/y)/sqrt(40)
varActual <- ((1/y)/sqrt(40))^2
table <- data.frame(StdDev = c(sdSim, sdActual),
                    Variance = c(varSim, varActual),
                    row.names = c("Simulated",
                                  "Theoretical"))

table
```
```{r}
## Calculate the difference between them
sdDiff <- sdSim - sdActual
varDiff <- varActual - varSim
```
The difference in standard devivation is `r sdDiff` and the variance is `r varDiff`. This show that the distribution between the simulated and theoretical are very similar. 

## 3.Show that the distribution is approximately normal.
```{r}
hist(meanSim, freq = F)
curve(dnorm(x, mean=actual, sd=sdActual), add = TRUE, col="red", lwd=2)
abline(v=actual, col= "green", lwd=2)
legend("topright", c("Theoretical Center", "Theoretical Distribution"), col=c("green", "red"), lwd=2)
```








```{r}
sessionInfo()
```